Gravitaitonal Wave Event Progenitor Synthesis

### 2022-05-25 src/tex/ms.tex
Will edited the 'graph on re-projection.

We reproject the recovered posterior to the observable
space, and compare the KL divergence between the original posterior and the
reprojected posterior. We compute KL divergence of the samples
obtained from root-finding alone as well as after the MCMC sampling procedure. %\wf{Clean up wording.}
For GW150914, the KL divergence between the reprojected posterior and the
original posterior is \kw{fill later} nats on average if we use the root-finding
result alone, whereas the MCMC result has a higher KL divergence at \kw{fill}
nats. The KL divergence stays stable for reprojecting with different random
seeds. In fig.\ref{fig:GW150914_reprojection}, we can see the reprojected
posterior from both the root-finding process alone and the MCMC result agrees
well with the original posterior, even though the agreement between the MCMC
result and the original posterior is not perfect. This degradation of the
agreement comes from the fact that we are using a KDE to estimate the posterior
density in the observable space. Note that the result from root-finding alone
and the result from MCMC agrees well in the evolutionary parameter space.
Compared to the result shown in a previous study, our result covers almost all
the posterior of GW150914 in the masses space, which means our result is more
consistent with the observation.

>>>>

It is interesting to re-project the posterior over progenitor ($\bm{\theta}'$)
and hyperparameters ($\bm{\lambda}$) using fresh random variables ($\bm{X}$) to
the observable space of GW parameters ($\bm{\theta}$).  Agreement between the
observed parameters and the re-projected parameters indicates good exploration
of the random variable space and lack of sensitivity to the details of these
random parameters.  Figure \ref{fig:GW150914_reprojection} shows good agreement
between the re-projected root-finding outputs as well as the re-projected MCMC
draws for our analysis of GW150914.  Unlike \citet{Andrews2021}, we find there
are no regions of observable space inaccessible to our evolutionary models; this
difference arises because we allow the evolutionary hyperparameters
$\bm{\lambda}$ to vary.
